Data 621---HW1---Regression Model---Version 2

### 2020-09-08 HW1/RegModel_Adler.Rmd
Complete the Box-Cox saga

```{r boxCox}
boxCox <- function(x, l) {
  if (l == 0) {
    log(x)
  } else {
    (x ^ l - 1) / l
  }
}

@@

TEAM_PITCHING_H <- -2.5
TEAM_FIELDING_E <- -0.5
TEAM_BASERUN_SB <- 0
TEAM_PITCHING_HR <- 0.6
TEAM_PITCHING_BB <- -0.15
TEAM_PITCHING_SO <- -0.35

```

# Build Models
## Task
Using the training data set, build at least three different multiple linear
regression models, using different variables (or the same variables with
different transformations). Since we have not yet covered automated variable
selection methods, you should select the variables manually (unless you
previously learned Forward or Stepwise selection, etc.). Since you manually
selected a variable for inclusion into the model or exclusion into [*sic*] the
model, indicate why this was done. Discuss the coefficients in the models, do
they make sense? For example, if a team hits a lot of Home Runs, it would be
reasonably expected that such a team would win more games. However, if the
coefficient is negative (suggesting that the team would lose more games), then
that needs to be discussed. Are you keeping the model even though it is counter
intuitive? Why? The boss needs to know.

@@

```{r loadPackages, echo=TRUE, eval=FALSE}
```
```{r readData, echo=TRUE, eval=FALSE}
```
```{r missingTable, echo=TRUE, eval=FALSE}
```
```{r summaryTable, echo=TRUE, eval=FALSE}
```
```{r boxPlot1, echo=TRUE, eval=FALSE}
```
```{r boxPlot2, echo=TRUE, eval=FALSE}
```
```{r corrgram, echo=TRUE, eval=FALSE}
```
```{r imputeMean, echo=TRUE, eval=FALSE}
```
```{r centerScale, echo=TRUE, eval=FALSE}
```
```{r plotScaled, echo=TRUE, eval=FALSE}
```

>>>>

```{r boxCox}
BxCox <- function(x, l) {
  ifelse(l == 0, log(x), (x ^ l - 1) / l)
}

@@

BCL <- data.table(Metric = c('TEAM_PITCHING_H', 'TEAM_FIELDING_E',
                             'TEAM_BASERUN_SB', 'TEAM_PITCHING_HR',
                             'TEAM_PITCHING_BB', 'TEAM_PITCHING_SO',
                             'TEAM_BATTING_3B'),
                  Lambda = c(-2.5, -0.5, 0, 0.6, -0.15, -0.35, 0))
setkey(BCL, Metric)
knitr::kable(BCL, digits = 2L, caption = 'Hand-selected Box-Cox Lambdas')

# Left join MBmelt to BCL. 
MBmelt <- BCL[MBmelt]

# Transform data where there are selected lambdas
MBmelt[!is.na(Lambda), Value := BxCox(Value, Lambda)]

# Remove TEAM_BATTING_HR

MBmelt <- MBmelt[Metric != 'TEAM_BATTING_HR']

# Plot results
ggplot(MBmelt, aes(x = Value)) + geom_density() +
  facet_wrap(~ Metric, scales = 'free') +
  ggtitle(label = 'Kernel-Smoothed Densities of Box-Cox Transformed Data')
```

Most of the variables are now closer to a Gaussian distribution. Also note we
have removed `TEAM_BATTING_HR` from the data. Now the data needs to be rescaled
and recentered.

```{r reScale}
MBmeltSC <- copy(MBmelt)
MBmeltSC[, Lambda := NULL]
MBmeltUnscale <- MBmeltSC[, .(Mean = mean(Value), SD = sd(Value)),
                          keyby = Metric]

MBmeltSC[, Value := scale(Value, center = TRUE, scale = TRUE), keyby = Metric]
knitr::kable(MBmeltUnscale, digits = 2L,
             caption = 'Post-Transform Data Means and SDs')
```

Unfortunately, the scaling introduces infinities, as most of the Box-Cox lamdas
are non-positive, which transforms 0 into infinity. These were converted to NAs
for the purposes of imputation, after which scaling and centering will be done
again. This is the danger of too many transforms. Each one induces a "stress" on
the relationship between the independent and dependent variables. At what point
does that relationship fracture?

```{r reImputeThenScale}
MBmeltSC <- copy(MBmelt)
MBmeltSC[, Lambda := NULL]
# Remove infinities
MBmeltSC[, Value := ifelse(is.infinite(Value), NA, Value)]
# Center and Scale
MBmeltSC[, Value := replace(Value, is.na(Value), mean(Value, na.rm = TRUE)),
       keyby = Metric]
MBmeltUnscale <- MBmeltSC[, .(Mean = mean(Value), SD = sd(Value)),
                          keyby = Metric]
MBmeltSC[, Value := scale(Value, center = TRUE, scale = TRUE), keyby = Metric]
knitr::kable(MBmeltUnscale, digits = 2L,
             caption = 'Final Post-Transform Data Means and SDs')
ggplot(MBmeltSC, aes(x = Value)) + geom_density() +
  facet_wrap(~ Metric, scales = 'free') +
  ggtitle(label = 'Kernel-Smoothed Densities of Scaled Box-Cox Transformed Data')
```
# Build Models
## Task
Using the training data set, build at least three different multiple linear
regression models, using different variables (or the same variables with
different transformations). Since we have not yet covered automated variable
selection methods, you should select the variables manually (unless you
previously learned Forward or Stepwise selection, etc.). Since you manually
selected a variable for inclusion into the model or exclusion into [*sic*] the
model, indicate why this was done. Discuss the coefficients in the models, do
they make sense? For example, if a team hits a lot of Home Runs, it would be
reasonably expected that such a team would win more games. However, if the
coefficient is negative (suggesting that the team would lose more games), then
that needs to be discussed. Are you keeping the model even though it is counter
intuitive? Why? The boss needs to know.

## Analysis

@@

```{r loadPackages, echo=TRUE, eval=FALSE}
```
```{r readData, echo=TRUE, eval=FALSE}
```
```{r missingTable, echo=TRUE, eval=FALSE}
```
```{r summaryTable, echo=TRUE, eval=FALSE}
```
```{r boxPlot1, echo=TRUE, eval=FALSE}
```
```{r boxPlot2, echo=TRUE, eval=FALSE}
```
```{r corrgram, echo=TRUE, eval=FALSE}
```
```{r imputeMean, echo=TRUE, eval=FALSE}
```
```{r centerScale, echo=TRUE, eval=FALSE}
```
```{r plotScaled, echo=TRUE, eval=FALSE}
```
```{r boxCox, echo=TRUE, eval=FALSE}
```
```{r reScale, echo=TRUE, eval=FALSE}
```
```{r reImputeThenScale, echo=TRUE, eval=FALSE}
```
